\textls[-0]{\thetitle}

### 2023-03-06 canonicitymodel.tex
Working on the appendix.

Then we extend the above model to \TT , we still start with the judgement.
The intuition of the model is similar to that of the consistency model---use the canonicity model of sigma type (from the earlier work) for linkage type and using Agda's inductive facility to justify our W-type.

The first observation is that, with this model, we know our system is consistent---we cannot derive $\goodTerm{\cdot}{t}{\bot}$. Otherwise, we have $\denotesC{\goodTerm{\cdot}{t}{\bot}}(\SubstEmp) = \sub{t}{\SubstEmp} \in \denotesS{\bot}(\star) = \emptyset$, that is an element in an empty set, a contradiction.

>>>>

Then we extend the above model to \TT , we still start with the judgement. Since linkage transformers are just syntactic sugar, we will not interpret it.
The intuition of the model is similar to that of the syntactic translation---use the canonicity model of sigma type (from the earlier work) for linkage type and using inductive facility in the meta-logic to justify our W-type.

\begin{align*}
  \denotesC{\goodSig{\Gm}{\_}{n}} & \text{ is a Set  and we define  } {\goodSigC{\Gm}{\sigma}{n}} :\iff \denotesC{\sigma} \in  \denotesC{\goodSig{\Gm}{\_}{n}} \\ 
  \denotesC{\goodWSig{\Gm}{\_}{n}} &\text{ is a set of list of pairs of type interpretation of length } n \\
  & \text{ and we define } \goodWSigC{\Gm}{\tau}{n} :\iff \denotesC{\goodWSig{\Gm}{\tau}{n}} \in \denotesC{\goodWSig{\Gm}{\_}{n}}
\end{align*}

The first observation is that, with this model, we know our system is consistent---we cannot derive $\goodTerm{\cdot}{t}{\bot}$. Otherwise, we have $\denotesC{\goodTerm{\cdot}{t}{\bot}}(\SubstEmp) = \sub{t}{\SubstEmp} \in \denotesC{\bot}(\star) = \emptyset$, that is an element in an empty set, a contradiction.

### 2023-03-06 metatheory2.tex
Working on canonicity model.
Working on the appendix.

% Copy and Paste Intuition of MLTT from other places to here
\subsection{Declarative Syntax for \TT : an MLTT variant with Linkages}
Compared to MLTT, \TT has 3 more judgements about signatures and linkage transformers.

@@

\subsection{Syntactic Translation get rid of Linkages}

@@

>>>>

% Copy and Paste Intuition of MLTT from other places to here
\subsection{Declarative Syntax for \TT : an MLTT variant with Linkages}
Compared to MLTT, \TT has 3 more judgements about signatures and linkage transformers. Moreover, the linkage transformer can be considered as a syntactic sugar (or library functions) and we will show how it can be translated away at the very end. 
Since it is a syntactic sugar, we will not consider about the linkage transformers during meta-theoretic reasoning.

@@

\subsection{Syntactic Translation to get rid of Linkages}

@@

\subsection{Syntactic Translation to get rid of Linkage Transformer}
